### 2013-09-13 mcmc.tex
marginalization

@@

...How is the sampling of the marginalized pdf trivially constructed from the full sampling?..

>>>>

% in the next paragraph I adopt $d$ to be the dimensionality of the space

@@

Finally---and perhaps most importantly---another magical propert of a sampling
  (in a $d$-dimensional space)
  is that if some of your $d$ dimensions are totally uninteresting
  (nuisance parameters, if you will)
  and some of your $d$ dimensions are of great interest,
  the sampling in the full $d$-space is trivially converted into a sampling in the subspace of interest:
You just drop from each $x_k$ vector (or blob or list) the dimensions of no interest!
That is, the projection of the sampling to the subspace of interest produces
  a sampling of the marginalized pdf, marginalizing (or projecting) out the nuisance parameters.
That is extremely important for inference,
  where there are always parameters with very different levels of importance to the scientific conclusions.
This point will return again below, either explicitly or implicitly. % does it?
